\tool: Revisiting BadUSB with Type-C

### 2021-01-27 WOOT/Files/related_work.tex
fix defence

From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which
are defined by protocol to transmitting data.  Without these pins, data can't
\fengwei{use "cannot" instead of "can't"} be transferred via USB cable. Based
on this fact, USB Condom \cite{Condom} is a hardware solution to block data
channel by adding blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leave power pins intact.  However, this method poses
a great challenge to plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.

Under the premise of ensuring the full functionality of USB devices, some works
try to improve the security during connection establishment.  Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices. But this requires users to have a
certain safety awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the USB device from unknown
sources to his/her whitelist without precaution. There are designs can overcome
this drawback. For instance, Mohammadmoradi et
al.\cite{mohammadmoradi2018making} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a safe and valid whitelist of USB devices. There is another work
mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
relies on rich experience of administrators to build a whitelist. However, some
modified USB devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use
future tense. We can just use present tense.} report the functionality claimed
by the device to user and let user decides whether to authorize. When a device
is plugged in, GoodUSB will load its driver but limit its functionality until a
series of authorizations is completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, it is impossible for an attacker to complete these authorization with
automatic script. Thus this defense is sufficient for normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB will be bypassed
easily as the attacker can just complete these authorization manually and
perform subsequent attacks.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attack.

@@

\fengwei{The table exceeds the max size.}
\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.52in] {Defence}{Attack} & \makecell*[c]{Facedancer\cite{facedancer},\\ Syzkaller\cite{syzkaller}} & \cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu},\cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
		\hline
		\makecell{USB condom \cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
		\hline
		\makecell{
			Windows Defender ATP\cite{windenfenderwhite}, \\
			Mohammadmoradi et al.\cite{mohammadmoradi2018making}, \\
			TMSUI\cite{yang2015tmsui}
		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\

		\hline
		\makecell{GoodUSB\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
		\hline

		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{JFCGuard\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull  \@ means that the defense is effective
	\item[2] \circlehalf \@ means that the defense is partial effective
	\item[3] \circleempty \@  means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of Defense against Different Attacks}
	\label{table:attack_vs_defense}
\end{table*}

>>>>

From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which
are defined by protocol to transmitting data.  Without these pins, data cannot
be transferred via USB cable. Based
on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
channel by adding blocker in the connector. This blocker can cut off the `D-'
and `D+' connection while leave power pins intact.  However, this method poses
a great challenge to plug-and-play property of USB, as once it is deployed, it
stops all USB functions other than charging.

Under the premise of ensuring the full functionality of USB devices, some works
try to improve the security during connection establishment.  Windows Defender
ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
on the whitelist are allowed to communicate with the host. This prevents all
potential attacks from untrusted devices. But this requires users to have a
certain safety awareness and technical background to maintain a valid
whitelist. For example, a naive user may add the USB device from unknown
sources to his/her whitelist without precaution. There are designs can overcome
this drawback. For instance, Mohammadmoradi et
al.~\cite{mohammadmoradi2018making} propose a strategy to generate such a
whitelist automatically. This strategy first generates a unique fingerprint for
each device based on its functionality. Then these fingerprints are used to
maintain a safe and valid whitelist of USB devices. There is another work
mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
relies on rich experience of administrators to build a whitelist. However, some
modified USB devices may hide their real functionality from the user.

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to user and let user decides whether to authorize. When a device
is plugged in, GoodUSB will load its driver but limit its functionality until a
series of authorizations is completed. These authorizations are designed to be
performed manually. As BadUSB is normally unable to obtain the video stream of
the host, it is impossible for an attacker to complete these authorization with
automatic script. Thus this defense is sufficient for normal BadUSB attack. But
if the attacker has the access to victim's screen, GoodUSB will be bypassed
easily as the attacker can just complete these authorization manually and
perform subsequent attacks.

@@

In addition to injection attacks, data theft attack is also one of the focuses
of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
exist an attack called JFC (juicy film charging)~\cite{JFC} which abuses the MHL
standard to steal video stream from the victim. In order to mitigate this
issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
like GPU/CPU usage to detect JFC attack.

@@

\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
\begin{table*}
	\centering
	\begin{tabular}{|c|c|c|c|c|c|c|c|}

		\hline
		\diagbox[width=1.52in,height=0.4in] {Defence}{Attack} & \makecell*[c]{Facedancer~\cite{facedancer},\\ Syzkaller~\cite{syzkaller}} &\cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC~\cite{JFC}&		\makecell{
			Duqu~\cite{duqu}, \\
			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
		\hline
		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
		\hline
		\makecell{
			Windows Defender ATP~\cite{windenfenderwhite}, \\
			Mohammadmoradi et al.~\cite{mohammadmoradi2018making}, \\
			TMSUI~\cite{yang2015tmsui}
		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\

		\hline
		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
		\hline

		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
		\hline
		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
			\hline
	\end{tabular}
	\linebreak
    \begin{tablenotes}
	\footnotesize
	\item[1] \circlefull  \@ means that the defense is effective
	\item[2] \circlehalf \@ means that the defense is partial effective
	\item[3] \circleempty \@  means that the defense is uneffective
	\end{tablenotes}
	\caption{Effectiveness of Defense against Different Attacks}
	\label{table:attack_vs_defense}
\end{table*}
